Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-02-14 paper.tex
Fix paragraph describing table

Table~\ref{tab:kink_fluting_params} summarises the quantitative differences
between the results for the two values of the resistivity $\eta$. \rev{The mean
across the radius of the ideal estimate of the growth
rate~\eqref{eq:fluting_growth_rate2} provides the theoretical average growth
rate, while the location of the peak growth rate provides a prediction of where
the instability will initially grow. This peak is used in conjunction with the
resonance equation~\eqref{eq:resonant_surface} (with $m=4$) to predict the most
unstable axial wavenumber.} The observed fluting wavenumbers are measured at
times just prior to the nonlinear development of the flute instability, that is
at $t=22$ when $\eta=10^{-3}$ and $t=26$ when $\eta = 10^{-4}$. The kink
wavenumber is measured at $t=26$ in both cases. These times allow fair
comparison between measurements. Also listed are estimates for the cumulative
heat generated via viscous and Ohmic heating during the simulation time. As is
also found in previous studies of viscous heating in kink
instabilities~\citep{quinnEffectAnisotropicViscosity2020}, anisotropic viscous
heating is approximately two orders of magnitude lower than isotropic and the
use of anisotropic viscosity enhances Ohmic heating.

The longitudinal wavenumber $k_{\text{kink}}$ of the observed kink perturbation
remains similar in both cases since the instability is essentially governed by
the twist injected by the driver which remains the same in both cases. In
contrast, the longitudinal wavenumber $k_{\text{flute}}$ of the observed
fluting perturbation is lower in the $\eta=10^{-3}$ cases. This is due to the
different resonant surface within which the perturbation grows, the location
being dictated by the peak of the linear \rev{flute growth rate $r_s$}. Note that the location of
this peak again matches well the location of the observed resonant surface, as
in the $\eta=10^{-4}$ cases. Similar to the $\eta=10^{-4}$ cases, the \rev{peak
growth rate $r_s$} predicted by the linear analysis is the same order of magnitude as
the observed growth rate.

>>>>

Table~\ref{tab:kink_fluting_params} summarises the quantitative differences
between the results for the two values of the resistivity $\eta$ and two models
of viscosity. \rev{The mean across the radius of the ideal estimate of the
growth rate~\eqref{eq:fluting_growth_rate2} provides the theoretical average
growth rate, which is in decent agreement with the observed rate in each case,
particularly in the more ideal case where $\eta=10^{-4}$. The location of the
peak growth rate provides a prediction of where the instability will initially
grow. This radius is used in conjunction with the resonance
equation~\eqref{eq:resonant_surface} (with $m=4$) to predict the axial
wavenumber of the perturbation with the greatest linear growth, i.e. the
perturbation most likely to be observed. Again, these are in good agreement
with the observed fluting wavenumbers, which are measured at times just prior
to the nonlinear development of the flute instability, that is at $t=22$ when
$\eta=10^{-3}$ and $t=26$ when $\eta = 10^{-4}$. The kink wavenumber is
measured at $t=26$ in both cases. Overall, the agreement between predicted and observed growth rates and perturbation wavenumbers allows us to conclude that the observed instability is the ideal flute instability and that the growth rate~\eqref{eq:fluting_growth_rate2} can be effectively applied to the instability within coronal loops.}

\rev{Also listed are estimates for
the cumulative heat generated via viscous and Ohmic heating during the
simulations. As is also found in previous studies of viscous heating in
kink instabilities~\citep{quinnEffectAnisotropicViscosity2020}, anisotropic
viscous heating is approximately two orders of magnitude lower than isotropic
and the use of anisotropic viscosity enhances Ohmic heating.}
